Concurrent Programming with CXL

### 2020-05-19 book/paper.tex
Latest
Author list...
Improved formatting

\title{Concurrent Programming with CXL}
\author{RVR and others}

@@

While the CXL machine does not have any built-in interlock instructions,
it does have support for executing multiple instructions atomically.
This feature is available in the CXL language through its \texttt{atomic}
statement.
You already saw an example of this in Figure~\ref{fig:petersonproof}.
We can use \texttt{atomic} blocks to implement a wide variety of
interlock operations.
For example, we could fix the program in Figure~\ref{fig:inc} by
constructing an atomic increment operation for a counter, like so:
\begin{code}
\begin{verbatim}
def atomic_inc(ptr):
    atomic:
        ^ptr = ^ptr + 1;
    ;
;
count = 0;
call atomic_inc(&(count));
\end{verbatim}
\end{code}

@@

>>>>

\title{Concurrent Programming with CXL}
\author{RVR and possibly others}

@@

While the CXL machine does not have any built-in interlock instructions,
it does have support for executing multiple instructions atomically.
This feature is available in the CXL language through its \texttt{atomic}
statement.
You already saw an example of this in Figure~\ref{fig:petersonproof}.
We can use \texttt{atomic} blocks to implement a wide variety of
interlock operations.
For example, we could fix the program in Figure~\ref{fig:inc} by
constructing an atomic increment operation for a counter, like so:
\begin{code}
\begin{verbatim}
def atomic_inc(ptr):
    atomic:
        ^ptr = ^ptr + 1;
    ;
;
count = 0;
call atomic_inc &(count);
\end{verbatim}
\end{code}

@@

\begin{quote}
Try doing mutual exclusion with other interlock instructions!
\begin{itemize}
\item Find a description for \texttt{compare-and-swap} on the internet and
update Figure~\ref{fig:tas}, replacing \texttt{tas}.
\item Other interesting interlock instructions include \texttt{swap} and
\texttt{fetch-and-add}.
\end{itemize}
\end{quote}
